### 2020-04-22 final_report/results.tex
minor edits to results

The first two experiments perform Bayesian optimisation to maximise~$R^2$ in
cross-validated setting as a function of model hyperparameters. While in the
first experiment we limit ourselves to the scope of a single slice of the
domain, in the second experiment we extend the process to the full feature
space.

The results displayed in~\cref{fig:exp1-time-vs-reg} indicate that in the first
experiment, gradient boosted trees clearly appear to be the most accurate as
well as the fastest surrogate class in terms of mean prediction time. Following
that, we note that extremely randomised trees, support vector machines and
neural networks also achieved satisfactory results in both examined metrics.
While the remainder of tested surrogate classes does not exhibit problems in
complexity, its regression performance falls below average.

@@

In the next experiment we examine surrogate scaling properties correlating
metrics of interest with progressively increasing training set size. The results
shown in~\cref{fig:scaling} seem to suggest that in terms of regression performance,
methods based on decision trees and neural networks offer the best accuracy on
larger sets overall. This is a curious extension of previous findings, where
gradient boosted trees were observed to significantly dominate over the rest of
the examined methods. With increasing training set size, their relative advantage is
clearly gradually diminished.

@@

According to our experiment, the lowest mean training time is generally achieved
by instance-based learning methods, which seem to offer near-constant scaling
characterists at the expense of significant performance increase later during
prediction. Following that, we observe that the majority of tree-based methods also exhibit
desirable properties. The notable exception here appear to be neural networks,
which are the only model to utilise parallelisation. As such, their constant
synchronisation overhead overall hinders performance on small training sets,
producing misleading results when divided by the number of samples.

@@

	\begin{subfigure}[b]{0.25\textwidth}
		\centering
		\includegraphics[width=\linewidth]{run1_5ke_1h3f128_4974_performance}
		% TODO: only a placeholder, regenerate when data becomes available
	\end{subfigure}\hfill%
	\begin{subfigure}[b]{0.25\textwidth}
		\centering
		\includegraphics[width=\linewidth]{run1_5ke_1h3f128_4974_performance}
		% TODO: only a placeholder, regenerate when data becomes available
	\end{subfigure}\hfill%
	\begin{subfigure}[b]{0.25\textwidth}
		\centering
		\includegraphics[width=\linewidth]{run1_5ke_1h3f128_4974_performance}
		% TODO: only a placeholder, regenerate when data becomes available
	\end{subfigure}\hfill%
	\begin{subfigure}[b]{0.25\textwidth}
		\centering
		\includegraphics[width=\linewidth]{run1_5ke_1h3f128_4974_performance}
		% TODO: only a placeholder, regenerate when data becomes available
	\end{subfigure}
	\caption{Regression performance of the best models trained in experiment~4.}
	\label{fig:reg-performance}
\end{figure}

@@

\begin{equation}
    TBR = mean_{i \in C} \left[ \frac{1 + sin(2*pi*n*(x_i - 1/2)) }{2} \right]
\end{equation}

plotted in~\cref{fig:sintoy} for $n=1$ and two continuous parameters $C$. ANNs trained on this model demonstrated similar performance to those on the expensive MC model. QASS performance was verified by training a 1h3f-256 ANN on the sinusoidal theory for varied quantities of initial, incremental, and MCMC candidate samples. Although the scope of this project did not include thorough searches of this hyperparameter domain, sufficient runs were made to identify some likely trends.

>>>>

The first two experiments perform Bayesian optimisation to maximise~$R^2$ in
cross-validated setting as a function of model hyperparameters. While in the
first experiment we limit training and testing sets to the scope of four slices of the
feature space, in the second experiment we lift this restriction.

The results displayed in~\cref{fig:exp1-time-vs-reg} indicate that in the first
experiment, gradient boosted trees clearly appear to be the most accurate as
well as the fastest surrogate class in terms of mean prediction time. Following
that, we note that extremely randomised trees, support vector machines and
neural networks also achieved satisfactory results with respect to both examined metrics.
While the remainder of tested surrogate classes does not exhibit problems in
complexity, its regression performance falls below average.

@@

In the next experiment we examine surrogate scaling properties correlating
metrics of interest with progressively increasing training set size. The results
shown in~\cref{fig:scaling} seem to suggest that in terms of regression performance,
methods based on decision trees and neural networks offer the best accuracy on
larger sets overall. This is a curious extension of the previous findings, where
gradient boosted trees were observed to significantly dominate over the rest of
the examined methods. With increasing training set size, their relative advantage is
clearly gradually diminished.

@@

According to our experiment, the lowest mean training time is generally achieved
by instance-based learning methods, which seem to offer near-constant scaling
characteristics at the expense of significant performance increase later during
prediction. Following that, we observe that the majority of tree-based methods also exhibit
desirable properties. The notable exception here appear to be neural networks,
which are the only model to utilise parallelisation. As such, their constant
synchronisation overhead presumably hinders performance on small training sets,
producing misleading results when divided by the number of samples.

@@

	\begin{subfigure}[b]{0.25\textwidth}
		\centering
		\includegraphics[width=\linewidth]{run1_5ke_1h3f128_4974_performance}
		% TODO: only a placeholder, regenerate when data becomes available
	\end{subfigure}\hfill%
	\begin{subfigure}[b]{0.25\textwidth}
		\centering
		\includegraphics[width=\linewidth]{run1_5ke_1h3f128_4974_performance}
		% TODO: only a placeholder, regenerate when data becomes available
	\end{subfigure}\hfill%
	\begin{subfigure}[b]{0.25\textwidth}
		\centering
		\includegraphics[width=\linewidth]{run1_5ke_1h3f128_4974_performance}
		% TODO: only a placeholder, regenerate when data becomes available
	\end{subfigure}\hfill%
	\begin{subfigure}[b]{0.25\textwidth}
		\centering
		\includegraphics[width=\linewidth]{run1_5ke_1h3f128_4974_performance}
		% TODO: only a placeholder, regenerate when data becomes available
	\end{subfigure}
	\caption{Regression performance of selected best-performing models trained in experiment~4.}
	\label{fig:reg-performance}
\end{figure}

@@

\begin{equation}
	\text{TBR} = \text{Mean}_{i \in C} \left[ \frac{1 + \sin(2\pi n (x_i - 1/2)) }{2} \right]
\end{equation}

plotted in~\cref{fig:sintoy} for $n=1$ and two continuous parameters $C$. ANNs
trained on this model demonstrated similar performance to those on the expensive
MC model. QASS performance was verified by training a $\text{1h3f}(256)$ ANN on
the sinusoidal theory for varied quantities of initial, incremental, and MCMC
candidate samples. Although the scope of this project did not include thorough
searches of this hyperparameter domain, sufficient runs were made to identify
some likely trends.
